### 2009-04-15 docs/runtime_parameters/runtime_parameters.tex
fixed the formatting of the tex file
now to make the description explicitly multiline, either add a "\newline" in
description, or use the shortcut "@@" which will be parsed by rp.py.
for example:

# 0 = Compute w0 at edges using a projection; @@
# 1 = Interpolate w0 to cell centers, then average to edges; @@
# 2 = Interpolate w0 to edges directly; @@
# 3 = Interpolate w0 to nodes, then average to edges.
w0mac_interp_type                   integer            1

or

# 0 = Compute w0 at edges using a projection; \newline
# 1 = Interpolate w0 to cell centers, then average to edges; \newline
# 2 =

\verb=  beta_type  = &   what type of coefficient to use inside the velocity divergence constraint. {\tt beta\_type} = 1 uses $\beta_0$; {\tt beta\_type} = 2 uses $\rho_0$ (anelastic); {\tt beta\_type} = 3 uses 1 (small-scale combustion).  &  1 \\

@@

\verb=  chk_int  = &   number of timesteps between writing a checkpoint file  &  0 \\

@@

\verb=  enthalpy_pred_type  = &   predict\_rhohprime = 1; predict\_h = 2; predict\_T\_then\_rhohprime = 3; predict\_T\_then\_h = 4; predict\_hprime = 5; predict\_Tprime\_then\_h = 6.  &  predict\_rhohprime \\

@@

\verb=  interp_type_radial_bin_to_cart  = &   The interpolation for filling a full multifab from a 1D bin-centered array. 1 = piecewise constant; 2 = piecewise linear.  &  1 \\

@@

\verb=  ppm_type  = &   0 = no ppm 1 = 1985 ppm 2 = 2009 ppm  &  0 \\

@@

\verb=  temp_diffusion_formulation  = &   How to compute the explicit thermal diffusion term. .true. = in terms of $T$; .false. = in terms of $\rho,p_0,X$.  &  .false. \\

@@

\verb=  w0mac_interp_type  = &   0 = Compute w0 at edges using a projection; 1 = Interpolate w0 to cell centers, then average to edges; 2 = Interpolate w0 to edges directly; 3 = Interpolate w0 to nodes, then average to edges.  &  1 \\

>>>>

\verb=  beta_type  = &   what type of coefficient to use inside the velocity divergence constraint. \newline {\tt beta\_type} = 1 uses $\beta_0$; \newline {\tt beta\_type} = 2 uses $\rho_0$ (anelastic); \newline {\tt beta\_type} = 3 uses 1 (small-scale combustion).  &  1 \\

@@

\verb=  chk_int  = &   Number of timesteps between writing a checkpoint file  &  0 \\

@@

\verb=  enthalpy_pred_type  = &   predict\_rhohprime = 1; \newline predict\_h = 2; \newline predict\_T\_then\_rhohprime = 3; \newline predict\_T\_then\_h = 4; \newline predict\_hprime = 5; \newline predict\_Tprime\_then\_h = 6.  &  predict\_rhohprime \\

@@

\verb=  interp_type_radial_bin_to_cart  = &   The interpolation for filling a full multifab from a 1D bin-centered array. \newline 1 = piecewise constant; \newline 2 = piecewise linear.  &  1 \\

@@

\verb=  ppm_type  = &   0 = no ppm \newline 1 = 1985 ppm \newline 2 = 2009 ppm  &  0 \\

@@

\verb=  temp_diffusion_formulation  = &   How to compute the explicit thermal diffusion term.  \newline .true. = in terms of $T$; \newline .false. = in terms of $\rho,p_0,X$.  &  .false. \\

@@

\verb=  w0mac_interp_type  = &   0 = Compute w0 at edges using a projection; \newline 1 = Interpolate w0 to cell centers, then average to edges; \newline 2 = Interpolate w0 to edges directly;                \newline 3 = Interpolate w0 to nodes, then average to edges.  &  1 \\
